Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-08 supp.rnw
Add short versions of the supplementary figure captions.
Adding xr-hyper breaks with siunitx commands in the captions.
The short captions don't feature any siunitx commands.
As such, this will allow adding xr-hyper.

\newcommand\modelfitplotcaption[1]{%
	\caption{%
		Plot of model fit using the #1.
		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
		The black line shows $y=x$.
	}%
}
\newcommand\partialresidualplotcaption[1]{%
	\caption{%
		Partial residual plots showing the effects of competition coefficients in the #1.
		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
		The black line shows, by its slope, the alpha value fitted by the model.
		The blue line shows a linear regression fitted to the plotted points, with \SI{95}{\percent} confidence interval.
	}%
}

>>>>

\newcommand\modelfitplotcaption[1]{%
	\caption[%
		Plot of model fit using the #1.
	]{%
		Plot of model fit using the #1.
		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
		The black line shows $y=x$.
	}%
}
\newcommand\partialresidualplotcaption[1]{%
	\caption[%
		Partial residual plots showing the effects of competition coefficients in the #1.
	]{%
		Partial residual plots showing the effects of competition coefficients in the #1.
		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
		The black line shows, by its slope, the alpha value fitted by the model.
		The blue line shows a linear regression fitted to the plotted points, with \SI{95}{\percent} confidence interval.
	}%
}
